Adaptative neighbouring methods applied to telephonic base stations

### 2024-09-03 article.tex
Centrage des auteurs

\title{Adaptative neighbouring methods applied to telephonic base stations}
\author{\IEEEauthorblockN{Paul MÉHAUD}\\
\IEEEauthorblockA{\textit{Intern at CTU in Prague} \\
\textit{INSA Rouen Normandie}\\
paul.mehaud@insa-rouen.fr}\\
\and
\IEEEauthorblockN{Brendan SÉVELLEC}\\
\IEEEauthorblockA{\textit{Intern at CTU in Prague} \\
\textit{INSA Rouen Normandie}\\
brendan.sevellec@insa-rouen.fr}}

>>>>

\title{Adaptative neighbouring methods applied to telephonic base stations}
\author{
    \begin{tabular}{cc}
        \IEEEauthorblockN{Paul MÉHAUD} & \IEEEauthorblockN{Brendan SÉVELLEC}\\
        \textit{Intern at CTU in Prague} & \textit{Intern at CTU in Prague}\\
        \textit{INSA Rouen Normandie} & \textit{INSA Rouen Normandie}\\
        paul.mehaud@insa-rouen.fr & brendan.sevellec@insa-rouen.fr\\
    \end{tabular}
}
